title: "Supplement: Neural representations of ambiguous affective stimuli and resilience to anxiety in emerging adults"
author: "Saragosa-Harris, N.M., et al."
date: "March 2023"
output:
  pdf_document:
    toc: true
    toc_depth: 4
header-includes:
    - \usepackage{caption}
    - \usepackage[singlelinecheck=false]{caption}
---
\captionsetup[table]{labelformat=empty}

---

```{r settings, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read_data, include=FALSE}
library(plyr)
library(psych)
library(dplyr)
library(tidyr)
library(stringr)
library(glue)
library(ggplot2)
library(lme4)
library(lmerTest)
library(kableExtra) # For formatting tables.
library(reshape2)
library(gtsummary) # also for summary tables.
library(patchwork)
library(ggeffects)
library(qwraps2)
library(broom) # for using "tidy" function.
library(broom.mixed)  # for using "tidy" function for lme4 models.
library(forcats) # For reversing levels of factors.
library(pander) # For formatting tables for t tests results.

options(qwraps2_markup = "markdown")
options(scipen=1, digits=2)

datadirectory <- '/Users/nataliesaragosa-harris/Library/CloudStorage/Box-Box/Natalie./UCLA./Lab./Studies/CollegeTransitionStudy/data/facestask/'
questionnaire_directory <- '/Users/nataliesaragosa-harris/Library/CloudStorage/Box-Box/Natalie./UCLA./Lab./Studies/CollegeTransitionStudy/data/questionnaires'

demographics <- read.csv('/Users/nataliesaragosa-harris/Library/CloudStorage/Box-Box/Natalie./UCLA./Lab./Studies/CollegeTransitionStudy/data/demographics.csv',stringsAsFactors = TRUE)
demographics <- demographics %>% select(Participant_ID,Sex,Age,race_combined,Hispanic,firstgeneration)
data <- read.csv(glue('{datadirectory}behavior_rsa_conditionlevel_shortdata.csv'),stringsAsFactors = TRUE) # Read in data.
long_behavioral_data <- read.csv(glue('{datadirectory}behavioral/BehavioralFacesTask_LongData.csv'),stringsAsFactors = TRUE)
fullsample_long_questionnairedata <- read.csv(glue('{questionnaire_directory}/anxiety/AnxietyData_LongFormat.csv'), header = TRUE)
lss_data <- read.csv(glue('{datadirectory}longdata_facestask_LSS_RSA_behavior.csv'),header = TRUE, stringsAsFactors = TRUE)
lss_data <- lss_data[!is.na(lss_data$response),] # Only keep trials in which they made a response.

actor_image_details <- read.csv(glue('{datadirectory}/actor_image_details_ctstask_radiate_sona.csv'), header = TRUE)

wide_anxiety_data <- read.csv(glue('{questionnaire_directory}/anxiety/CTS_T1_T2_T3_T4_T5_AnxietyOnly.csv'), header = TRUE)
wide_anxiety_data <- wide_anxiety_data %>% select(Participant_ID,contains("ANXTOTAL"))
colnames(wide_anxiety_data) <- gsub("SAARED_ANXTOTAL", "anxiety_total", colnames(wide_anxiety_data))
# Get quarantine timepoint data as well.
timepoint_data <- read.csv(glue('{questionnaire_directory}/anxiety/quarantine_timepoint_data.csv'), header = TRUE)
timepoint_data$quarantine_onset_factor <- as.factor(timepoint_data$quarantine_onset_factor)
quarantine_timepoint_data <- timepoint_data %>% select(Participant_ID,quarantine_onset_factor)

mstat_data <- read.csv(glue('{questionnaire_directory}/mstat/CTS_MSTAT_Scored.csv'), header = TRUE)
mstat_data$mstat_total_score_z <- scale(mstat_data$mstat_total_score, center = TRUE)[,]
mstat_data <- mstat_data %>% select(Participant_ID,mstat_total_score,mstat_total_score_z)
data$mstat_total_score_z <- scale(data$mstat_total_score, center = TRUE)[,]
data$Percent_Surprised_Positive_Z <- scale(data$Percent_Surprised_Positive,center=TRUE)[,]

valence_bias <- data[,c("Participant_ID","Percent_Surprised_Negative","Percent_Surprised_Negative_Z","Percent_Surprised_Positive","Percent_Surprised_Positive_Z")]

fullsample_questionnairedata <- merge(wide_anxiety_data,mstat_data, by = "Participant_ID")
fullsample_questionnairedata <- merge(fullsample_questionnairedata,quarantine_timepoint_data, by = "Participant_ID")
fullsample_questionnairedata <- merge(fullsample_questionnairedata,demographics, by = "Participant_ID")
fullsample_questionnairedata <- merge(fullsample_questionnairedata,valence_bias, by = "Participant_ID", all.x=TRUE) # Will have NA values for those who did not do the MRI task.
t1_baseline_date <- subset(fullsample_long_questionnairedata,timepoint=="T1")
t1_baseline_date <- t1_baseline_date  %>% select(Participant_ID, T1_overall_timepoint)
fullsample_questionnairedata <- merge(fullsample_questionnairedata,t1_baseline_date, by = "Participant_ID",all.x=TRUE,all.y=FALSE)

fullsample_long_questionnairedata <- merge(fullsample_long_questionnairedata,mstat_data, by = "Participant_ID", all.x=TRUE)
fullsample_long_questionnairedata <- merge(fullsample_long_questionnairedata,valence_bias, by = "Participant_ID", all.x=TRUE)
fullsample_long_questionnairedata <- merge(fullsample_long_questionnairedata,quarantine_timepoint_data, by = "Participant_ID", all.x=TRUE)
fullsample_long_questionnairedata$participant_month <- fullsample_long_questionnairedata$participant_specific_timepoint/30 # For models in which days are too large and values need to be rescaled.

conditionlevel_rsa_data <- data[,grepl(glob2rx('Participant_ID|*average_amy*fisher_z'), names(data))]
fullsample_long_questionnairedata <- merge(fullsample_long_questionnairedata,conditionlevel_rsa_data, by = "Participant_ID", all.x=TRUE)

#mstat_data_z <- mstat_data %>% select(Participant_ID,mstat_total_score_z) # For merging with MRI data.
#data <- merge(data,mstat_data_z, by = "Participant_ID")
#fullsample_long_questionnairedata <- merge(fullsample_long_questionnairedata,mstat_data_z, by = "Participant_ID")

# Add z scores to the data.
data$angry_rt_average_z <- scale(data$angry_rt_average, center = TRUE)[,]
data$surprised_rt_average_z <- scale(data$surprised_rt_average, center = TRUE)[,]
data$happy_rt_average_z <- scale(data$happy_rt_average, center = TRUE)[,]
data$rt_difference_all_positive_vs_negative_z <- scale(data$rt_difference_all_positive_vs_negative, center = TRUE)[,]
data$rt_difference_positive_vs_negative_surprised_z <- scale(data$rt_difference_positive_vs_negative_surprised, center = TRUE)[,]
data$rt_difference_surprised_vs_angry_z <- scale(data$rt_difference_surprised_vs_angry, center = TRUE)[,]
data$rt_difference_surprised_vs_happy_z <- scale(data$rt_difference_surprised_vs_happy, center = TRUE)[,]
data$rt_difference_surprised_vs_unambiguous_z <- scale(data$rt_difference_surprised_vs_unambiguous, center = TRUE)[,]
data$surprised_negative_rating_rt_average_z <- scale(data$surprised_negative_rating_rt_average, center = TRUE)[,]
data$surprised_positive_rating_rt_average_z <- scale(data$surprised_positive_rating_rt_average, center = TRUE)[,]
data$all_negative_rating_rt_average_z <- scale(data$all_negative_rating_rt_average, center = TRUE)[,]
data$all_positive_rating_rt_average_z <- scale(data$all_positive_rating_rt_average, center = TRUE)[,]

# Behavioral trial level data: Edit response so that a positive rating = 0 and a negative rating = 1.
long_behavioral_data <- long_behavioral_data %>%
  mutate(response = case_when(P_N_response =="P" ~ 0,
                              P_N_response =="N" ~ 1))
# Only keep trials in which there is a response.
long_behavioral_data <- long_behavioral_data[complete.cases(long_behavioral_data$response),]
anxiety <- data %>% select(Participant_ID,anxiety_total_T1,Anxiety_Total_T1_Z)
long_behavioral_data <- merge(long_behavioral_data,anxiety,all.x=TRUE)
surprised_trials <- subset(long_behavioral_data, TrialType == "surprised")

```

```{r plot_themes, include=FALSE}
#Theme for plots.
nsh_theme <- theme(#text = element_text(family = "Avenir"), # Doesn't work with PDF I think.
                   title = element_text(size=14, vjust=2, face="bold"),
                   plot.subtitle = element_text(size=12,color="gray40", face="bold.italic"),
                   axis.title.x= element_text(size=12, vjust=-0.3),
                   axis.title.y= element_text(size=12, vjust=1.5),
                   axis.text.x= element_text(size=12, colour="black"),
                   axis.text.y= element_text(size=12, colour="black"),
                   strip.text = element_text(size=12, face="bold"),
                   panel.background = element_blank(),
                   axis.line = element_line(colour = "black"))

# General color for plots with anxiety as the outcome: "#8AAB98".

# Color dictionary for box plots with different comparison types.
condition_comparison_colors <- c("threatening/ambiguous" = "#C5776C", # rust.
                "nonthreatening/ambiguous" = "#A09CB0", # purple.
                "threatening/nonthreatening" = "#EBCC2A") # yellow.


actor_plots_theme <- theme(#text = element_text(family = "Avenir"),        
                   title = element_text(size=8, vjust=2, face="bold"),
                   plot.subtitle = element_text(color="gray40", size=8, face="bold.italic"),
                   axis.title.x= element_text(size=8, vjust=-0.3),
                   axis.title.y= element_text(size=8, vjust=1.5),
                   axis.text.x= element_text(size=4, colour="black", angle = 90, vjust = 0.5, hjust=1), # Rotate x axis labels.
                   axis.text.y= element_text(size=12, colour="black"),
                   strip.text = element_text(size=8, face="bold"),
                   panel.background = element_blank(),
                   axis.line = element_line(colour = "black"))

```

```{r define_table_functions, include=FALSE}

# Define functions to get the coefficients, statistics, confidence intervals, from 
# different types of regression models and print them in a formatted table.

#Removed from functions.
  # Format confidence intervals and add to model data frame.
  # Do not need to do this part if tidy(conf.int=TRUE) works.
  #ci <- as.data.frame(confint(lm_model))
  #ci$term = row.names(ci)
  #ci$upper <- round(ci$`97.5 %`, digits = 2)
  #ci$lower <- round(ci$`2.5 %`, digits = 2)
  #ci$CI <- glue('[{model_df$conf.low}, {model_df$conf.high}]')
  #ci <- ci %>% select(term,CI)
  # Save formatted CI to model dataframe.
 # model_df <- merge(model_df,ci)


# Pass in a linear model, a list of labels for the coefficients, and dependent variable name.
print_regression_table <- function(lm_model,model.terms.labels,dv){
  model_df <- lm_model %>% tidy(conf.int=TRUE,effects="fixed") %>% mutate(p.value = scales::pvalue(p.value),
                                                                          conf.high = round(conf.high,digits=2),
                                                                          conf.low = round(conf.low,digits=2))# Format model information as a dataframe.
  df <- lm_model$df.residual # Manually get degrees of freedom (no degrees of freedom when use tidy() with a lm model).
  model_df$CI <- glue('[{model_df$conf.low}, {model_df$conf.high}]')
  
  
  # Order columns.
  model_df <- model_df %>% select("term","estimate","std.error","CI","statistic","p.value") # No degrees of freedom when use tidy() with a lm model.
  model_df <- model_df %>% mutate(term = model.terms.labels)
  colnames(model_df) <- c("variable","estimate", "SE", "CI",glue("t({df})"), "p")
  #model_df$p.value <- round(model_df$p.value,digits = 4)

  kable(model_df,
        escape = FALSE,
        format="latex",
        caption = glue("Dependent variable: {dv}"),
        align = "l",
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15") %>%
  kable_styling(position = "left")
      
}

# Do a different function for multilevel linear models since the output is slightly different (e.g., includes degrees of freedom for each coefficient).
# Pass in a multilevel model, a list of labels for the coefficients, and dependent variable name.
print_multilevel_table <- function(mlm_model,model.terms.labels,dv){
  model_df <- mlm_model %>% broom.mixed::tidy(conf.int=TRUE,effects="fixed") %>% mutate(p.value = scales::pvalue(p.value),
                                                                                        df = round(df, digits= 10),
                                                                                        conf.high = round(conf.high,digits=2),
                                                                                        conf.low = round(conf.low,digits=2))# Format model information as a dataframe.
  model_df$CI <- glue('[{model_df$conf.low}, {model_df$conf.high}]')
  
  # Order columns.
  model_df <- model_df %>% select("term","estimate","std.error","CI","statistic","df","p.value")
  model_df <- model_df %>% mutate(term = model.terms.labels)
  colnames(model_df) <- c("variable","estimate", "SE", "CI","t", "df","p")

  kable(model_df,
        format="latex",
        escape = FALSE,
        caption = glue("Fixed effects from multilevel model\\\\Dependent variable: {dv}"),
        align = "l",
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15") %>%
  kable_styling(position = "left")
      
}


# Do a different function for multilevel logistic models since the output is slightly different and the estimates are logit and odds ratios.
# Pass in a multilevel logistic model, a list of labels for the coefficients, and region name.
print_multilevel_logistic_table <- function(mlm_log_model,model.terms.labels,region){
    # Note: using exponentiate = TRUE to make logit value an odds ratio instead.
  model_df <- mlm_log_model %>% broom.mixed::tidy(conf.int=TRUE,exponentiate = TRUE, effects="fixed") %>% mutate(p.value = scales::pvalue(p.value),
                                                                                                             #df = round(df, digits= 10),
                                                                                                             conf.high = round(conf.high,digits=2),
                                                                                                             conf.low = round(conf.low,digits=2))# Format model information as a dataframe.
  model_df$CI <- glue('[{model_df$conf.low}, {model_df$conf.high}]')
  
  # Order columns.
  model_df <- model_df %>% select("term","estimate","std.error","CI","statistic","p.value")
  model_df <- model_df %>% mutate(term = model.terms.labels)
  colnames(model_df) <- c("variable","odds ratio", "SE", "CI","z","p") # odds ratio instead of estimate, statistic is a z value, doesn't have degrees of freedom included I think?

  kable(model_df,
        escape = FALSE,
        format="latex",
        caption = glue("Fixed effects from multilevel logistic model\\\\ Region: {region}\\\\Dependent variable: Likelihood positive categorization"), # Should print "right amygdala" or "left amygdala".
        align = "l",
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15") %>%
  kable_styling(position = "left")
      
}




```
\newpage
# Sample information.
## *Supplemental Table 1a: Sample demographics and summary statistics for questionnaire data.*
```{r sample_information,include=FALSE, warning = FALSE}

summary_data <- fullsample_questionnairedata %>% select(Age, Sex, race_combined,Hispanic,firstgeneration, anxiety_total_T1, Percent_Surprised_Negative, mstat_total_score)

```

```{r sample_information_table,echo=FALSE, warning = FALSE, results = 'asis'}

sample_information_table <- summary_data %>%
                           tbl_summary(label = c(Percent_Surprised_Negative ~ "Negative valence bias",
                                       anxiety_total_T1 ~ "Baseline anxiety",
                                       mstat_total_score ~ "Self-reported ambiguity tolerance",
                                       race_combined ~ "Race",
                                       Hispanic ~ "Ethnicity",
                                       firstgeneration ~ "First generation college student"),
                                       missing= "no") %>% #,
                                       #type = list(firstgeneration ~ "categorical"))  %>% # To have it print both "yes" and "no" need to have this.
                                        add_n() %>%
                                          modify_header(label ~ "**Variable**") %>%
                                            modify_header(update = stat_0 ~ " ") %>% # Removethe "N = 101" from the table, print individual N values for each variable instead.
                                              bold_labels()

sample_information_table %>% as_hux_table()

#as_gt() 
# convert to gt table

#as_gt(sample_information_table) %>% gt::as_latex()

#knitr::knit_print(sample_information_table) %>% gt::as_latex()

```
\newpage
## *Supplemental Table 1b: Number of complete observations (participants) at each timepoint.*
```{r number_longitudinal_observations_table,echo=FALSE, warning = FALSE, results = 'asis'}

timepoint_summary_table <- timepoint_data %>% summarise(T1 = sum(as.numeric(!is.na(date_standard_T1))),
                                                        T2 = sum(as.numeric(!is.na(date_standard_T2))),
                                                        T3 = sum(as.numeric(!is.na(date_standard_T3))),
                                                        T4 = sum(as.numeric(!is.na(date_standard_T4))),
                                                        T5 = sum(as.numeric(!is.na(date_standard_T5))))
  kable(timepoint_summary_table,
        escape = FALSE,
        caption = glue("Number of anxiety observations at each timepoint"),
        align = "l",
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15")

```

## *Supplemental Table 1c: Number of completed timepoints by demographics.*
```{r number_longitudinal_observations_demographics_table,echo=FALSE, warning = FALSE, results = 'asis'}

timepoint_data  <- merge(timepoint_data,demographics,by="Participant_ID")
timepoint_data$complete_timepoints <- as.factor(timepoint_data$complete_timepoints)

sex_complete_timepoints <- chisq.test(timepoint_data$Sex, timepoint_data$complete_timepoints)
#sex_complete_timepoints$observed
race_complete_timepoints <-chisq.test(timepoint_data$race_combined, timepoint_data$complete_timepoints)
#race_complete_timepoints$observed
ethnicity_complete_timepoints <-chisq.test(timepoint_data$Hispanic, timepoint_data$complete_timepoints)
#ethnicity_complete_timepoints$observed
firstgeneration_complete_timepoints <-chisq.test(timepoint_data$firstgeneration, timepoint_data$complete_timepoints)
#firstgeneration_complete_timepoints$observed

complete_timepoints_by_demographics <-  data.frame("Variable"  = c("Sex","Race","Ethnicity","First generation (yes/no)"),
             "Chi squared" = c(as.numeric(sex_complete_timepoints$statistic),
                                    as.numeric(race_complete_timepoints$statistic),
                                    as.numeric(ethnicity_complete_timepoints$statistic),
                                    as.numeric(firstgeneration_complete_timepoints$statistic)),
            "df" = c(as.numeric(sex_complete_timepoints$parameter),
                                    as.numeric(race_complete_timepoints$parameter),
                                    as.numeric(ethnicity_complete_timepoints$parameter),
                                    as.numeric(firstgeneration_complete_timepoints$parameter)),
            "p value" = c(as.numeric(sex_complete_timepoints$p.value),
                                    as.numeric(race_complete_timepoints$p.value),
                                    as.numeric(ethnicity_complete_timepoints$p.value),
                                    as.numeric(firstgeneration_complete_timepoints$p.value)))


  kable(complete_timepoints_by_demographics,
        escape = FALSE,
        format="latex",
        caption = "Results from chi square tests of independence testing association between number of completed timepoints to demographic variables.",
        align = "l",
        booktabs = TRUE,
        longtable = TRUE,
        linesep = "")  %>%
        row_spec(0,bold=TRUE) %>% 
        kableExtra::kable_styling(
        position = "left",
        latex_options = c("striped", "repeat_header"),
        stripe_color = "gray!15") %>%
  kable_styling(position = "left")
  
```

# Longitudinal anxiety scores.
## *Supplemental Table 2: Growth curve model of anxiety scores over time.*
```{r longitudinal_anxiety_analysis, include=FALSE, warning = FALSE}
# Use participant_month (months) instead of participant_specific_timepoint (days) because otherwise model does not converge (values are too large).

# Does the addition of random slopes to the model significantly improve model fit?
# likelihood ratio test with mixture chi-square (chibar) distribution needed for testing if variances = 0
# test random slope vs. random intercept models.
# requires refitting models using FIML estimation.
# unload lmerTest package or bug in varTestnlme causes an error.
detach(package:lmerTest)
library(varTestnlme)
modelone.fiml <- lmer(anxiety_total ~ participant_month + (1 + participant_month | Participant_ID), data = fullsample_long_questionnairedata, REML=FALSE)
#summary(modelone.fiml)
randomintercept.fiml <- lmer(anxiety_total ~ participant_month + (1 | Participant_ID), data = fullsample_long_questionnairedata, REML=FALSE)
#summary(randomintercept.fiml)
varCompTest(modelone.fiml, randomintercept.fiml, pval.comp = "bounds")

# The likelihood ratio test is significant (LRT = 28, p < 0.001), indicating that we can reject the null hypothesis that the models with and without the random slope show the same degree of fit for the data. Therefore, we can conclude that the random slope model is a better fit for the data than the random intercept model that does not include random slopes. That is, including the random slopes (i.e., allowing the effect of time on anxiety to vary between participants) improves the fit of the model relative to a simpler model that includes random intercepts but no random slopes (i.e., the effect of time on anxiety is fixed across all participants).


library(lmerTest)
modelone_month <-  lmer(anxiety_total ~ participant_month + (1 +  participant_month | Participant_ID), data = fullsample_long_questionnairedata, REML = TRUE) # No convergence error here.
#summary(modelone_month)
#confint(modelone_month)
# No fixed effect of time.
# beta = -0.01, 95% CI [-0.47,0.45], t(80.67)= -0.03, p = 0.97.

# Get participant-specific slopes.
anxiety_slopes <- coef(modelone_month)$Participant_ID
anxiety_slopes$Participant_ID <- rownames(anxiety_slopes)
rownames(anxiety_slopes) <- 1:nrow(anxiety_slopes)
anxiety_slopes <- plyr::rename(anxiety_slopes, c("participant_month" = "participant_month_slope",
                                                 "(Intercept)" = "participant_intercept"))
# Add these slopes to the data.
data <- merge(data,anxiety_slopes,by = "Participant_ID")


# Control for  time of quarantine onset relative to a participant’s timeline (a between-subjects factor, corresponding to whether the quarantine began between their T1 and T2 timepoints, or between their T2 and T3 timepoints, etc.).
modelone_month_control_quarantine_timepoint <-  lmer(anxiety_total ~ participant_month +  quarantine_onset_factor + (1 +  participant_month | Participant_ID), data = fullsample_long_questionnairedata, REML = TRUE) # No convergence error here.
#summary(modelone_month_control_quarantine_timepoint)
#confint(modelone_month_control_quarantine_timepoint)
# No fixed effect of time.
# beta = 0.001, 95% CI [-0.46,0.46], t(80.57) =  0.01, p = 0.995.

```

```{r longitudinal_anxiety_table, echo=FALSE, warning = FALSE}
print_multilevel_table(modelone_month,
                        c("Intercept", "Time (months)"),
                       "Anxiety score")
```

## *Supplemental Table 3: Growth curve model of anxiety scores over time, controlling for quarantine onset.*
```{r longitudinal_anxiety_control_table, echo=FALSE, warning = FALSE}

print_multilevel_table(modelone_month_control_quarantine_timepoint,
                        c("Intercept", "Time (months)",
                          "Quarantine onset between T1 and T2",
                          "Quarantine onset between T2 and T3",
                          "Quarantine onset between T3 and T4",
                          "Quarantine onset between T4 and T5"),
                       "Anxiety score")
```

```{r anxiety_variations_within_participant,include=FALSE, warning = FALSE}
# What is the range of within-person variation (standard deviations) in anxiety scores across the timepoints?
anxiety_variations <- fullsample_long_questionnairedata %>%
  group_by(Participant_ID) %>%
  summarise(variation_anxiety = sd(anxiety_total, na.rm=TRUE))


#View(anxiety_variations) # CTS002 and CTS035, and CTS061 do not have a standard deviation (I think because these are the three participants who only completed one timepoint).
#mean(anxiety_variations$variation_anxiety, na.rm = TRUE) # 6.1
#range(anxiety_variations$variation_anxiety, na.rm = TRUE) # 1.5 to 16.8.

#Across participants and timepoints, SCAARED scores ranged from 0 to 85 overall. Within participants, anxiety scores appeared to be relatively stable, with an average within-person standard deviation in scores of 6.1 (range = 1.5 to 16.8).
#mean(fullsample_long_questionnairedata$anxiety_total, na.rm = TRUE)
#range(fullsample_long_questionnairedata$anxiety_total, na.rm = TRUE)

```

# Self-reported ambiguity tolerance and anxiety.
## *Supplemental Table 4: Self-reported ambiguity tolerance and baseline anxiety.*
```{r anxiety_mstat,echo=FALSE, include=FALSE}
anxiety_mstat_t1 <- lm(scale(anxiety_total_T1) ~ scale(mstat_total_score), data = fullsample_questionnairedata)
#summary(anxiety_mstat_t1)
#confint(anxiety_mstat_t1, 'scale(mstat_total_score)', level=0.95)
# mstat estimate = -0.32, 95% CI [-0.51, -0.13], t(99) = -3.35, p < 0.01.

```

```{r anxiety_mstat_table,echo=FALSE}
print_regression_table(anxiety_mstat_t1,
                        c("Intercept", "MSTAT score (z)"),
                       "Baseline anxiety score (z)")
```

## *Supplemental Table 5: Self-reported ambiguity tolerance and longitudinal anxiety.*
```{r anxiety_mstat_longitudinal,echo=FALSE, include=FALSE}

# Do longitudinal changes in anxiety (i.e., the relation between time and anxiety) differ as a function of self-reported ambiguity tolerance?
interaction_mstat_longitudinal_anxiety <- lmer(anxiety_total ~ participant_month +  mstat_total_score_z + (participant_month*mstat_total_score_z) + (1 + participant_month | Participant_ID), data = fullsample_long_questionnairedata)
#summary(interaction_mstat_longitudinal_anxiety, ddf = "Kenward-Roger") # Fixed effect of MSTAT but no interaction.
#confint(interaction_mstat_longitudinal_anxiety)
# interaction beta = 0.2, 95% CI [-0.25,0.64], t(86.75) =  0.88, p =  0.38.
# mstat beta = -5.05, 95% CI [-8.12, -1.98], t(98.63) = -3.22, p < 0.01.

# Test with maximum likelihood instead?
interaction_mstat_longitudinal_anxiety <- lmer(anxiety_total ~ participant_month +  mstat_total_score_z + (participant_month*mstat_total_score_z) + (1 + participant_month | Participant_ID), data = fullsample_long_questionnairedata,  REML = FALSE)
# Note: Kenward-Roger is only available for REML model fits?
#summary(interaction_mstat_longitudinal_anxiety) # Fixed effect of MSTAT but no interaction.


```

```{r anxiety_mstat_longitudinal_table, echo=FALSE, warning = FALSE}
print_multilevel_table(interaction_mstat_longitudinal_anxiety,
                        c("Intercept","Time (months)","MSTAT score (z)","Time x MSTAT score (z)"),
                       "Anxiety score")

```

# Behavior in post-scan task.
## *Supplemental Table 6a: Accuracy for non-ambiguous (threatening and nonthreatening) images in post-scan task.*
```{r postscan_task_accuracy,include=FALSE}

accuracy_data <- data %>% select(Participant_ID, Percent_Angry_Correct, Percent_Happy_Correct) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "accuracy")

accuracy_data$trial_type <- str_replace(accuracy_data$trial_type, "Percent_", "")
accuracy_data$trial_type <- str_replace(accuracy_data$trial_type, "_Correct", "")

# One-tailed t-test to make sure accuracy is greater than 50% (chance accuracy).
percent_angry_correct = t.test(data$Percent_Angry_Correct, mu = 0.50, alternative = "greater") # mean accuracy = 0.93; t(40) = 31; p < 0.001.
percent_happy_correct = t.test(data$Percent_Happy_Correct, mu = 0.50, alternative = "greater") # mean accuracy = 0.96; t(40) = 72; p < 0.001.

```
 
```{r postscan_task_accuracy_table,echo=FALSE, warning=FALSE}
pander(percent_angry_correct, caption = "One-tailed t-test: Is average accuracy for threatening (angry) images greater than 50% (chance accuracy)?")
pander(percent_happy_correct, caption = "One-tailed t-test: Is average accuracy for nonthreatening (happy) images greater than 50% (chance accuracy)?")
```

## *Supplemental Table 6b: Reaction time by image type in post-scan task.*
```{r angry_happy_reactiontime,echo=FALSE, warning = FALSE}

reactiontime_average_data <- data %>% select(Participant_ID, angry_rt_average, happy_rt_average,surprised_rt_average) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_average")

reactiontime_sd_data <- data %>% select(Participant_ID, angry_rt_sd, happy_rt_sd, surprised_rt_sd) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_sd")

reactiontime_average_data$trial_type <- str_replace(reactiontime_average_data$trial_type, "_rt_average", "")
reactiontime_average_data$trial_type <- as.factor(reactiontime_average_data$trial_type)
reactiontime_sd_data$trial_type <- str_replace(reactiontime_sd_data$trial_type, "_rt_sd", "")
reactiontime_sd_data$trial_type <- as.factor(reactiontime_sd_data$trial_type)

reactiontime_data <- merge(reactiontime_average_data,reactiontime_sd_data,by=c("Participant_ID","trial_type"))

# Make surprised the reference level,so that angry and happy are being compared to surprised (as this is where we expect to see the difference).
reactiontime_by_trialtype <- lm(reactiontime_average ~ relevel(trial_type, ref = "surprised"), data = reactiontime_data)
#summary(reactiontime_by_trialtype)
#anova(reactiontime_by_trialtype)

# Paired t test between conditions.
t.test(data$angry_rt_average,data$surprised_rt_average, paired = TRUE, alternative = "two.sided")
t.test(data$happy_rt_average,data$surprised_rt_average,paired = TRUE, alternative = "two.sided")


```

```{r angry_happy_reactiontime_table,echo=FALSE, warning = FALSE}
print_regression_table(reactiontime_by_trialtype,
                        c("Intercept", "Angry trials","Happy trials"),
                       "Average reaction time (surprised trials are reference level)")

anova(reactiontime_by_trialtype)

```

# Self-reported ambiguity tolerance and behavior in post-scan task.
## *Supplemental Table 7a: Self-reported ambiguity tolerance and negative valence biases in post-scan task.*
```{r mstat_negativity_bias,include=FALSE}
mstat_percent_surprised_negative <- lm(Percent_Surprised_Negative_Z ~ mstat_total_score_z, data = data)
#summary(mstat_percent_surprised_negative)
#confint(mstat_percent_surprised_negative, 'mstat_total_score_z', level=0.95)
# MSTAT estimate = 0.14, 95% CI [ -0.18,0.46], t(39) = 0.91, p = 0.37.

```

```{r mstat_negativity_table,echo=FALSE, warning=FALSE}
print_regression_table(mstat_percent_surprised_negative,
                        c("Intercept", "MSTAT score (z)"),
                       "Negative valence bias (z)")

```

## *Supplemental Table 7b: Same model with low accuracy participant removed.*
```{r mstat_negativity_bias_sensitivityanalysis,include=FALSE}
mstat_percent_surprised_negative_sensitivityanalysis <- lm(Percent_Surprised_Negative_Z ~ mstat_total_score_z, data = subset(data,Participant_ID!="P_070"))

```

```{r mstat_negativity_sensitivityanalysis_table,echo=FALSE, warning=FALSE}
print_regression_table(mstat_percent_surprised_negative_sensitivityanalysis,
                        c("Intercept", "MSTAT score (z)"),
                       "Negative valence bias (z)")
```

# Anxiety and behavior in post-scan task.
## *Supplemental Table 8a: Negative valence biases and baseline anxiety scores.*
```{r anxiety_negativity_bias,include=FALSE,warning=FALSE}
anxiety_percent_surprised_negative <- lm(Percent_Surprised_Negative_Z ~ scale(anxiety_total_T1), data = data)
#summary(anxiety_percent_surprised_negative)
# p = 0.70.
```

```{r anxiety_negativity_bias_table,echo=FALSE,warning=FALSE}
print_regression_table(anxiety_percent_surprised_negative,
                        c("Intercept", "Baseline anxiety (z)"),
                       "Negative valence bias (z)")
```

## *Supplemental Table 8b: Same model with low accuracy participant removed.*
```{r anxiety_negativity_bias_sensitivityanalysis,include=FALSE,warning=FALSE}
anxiety_percent_surprised_negative_sensitivityanalysis <- lm(Percent_Surprised_Negative_Z ~ scale(anxiety_total_T1), data = subset(data,Participant_ID!="P_070"))

```

```{r anxiety_negativity_bias_sensitivityanalysis_table,echo=FALSE,warning=FALSE}
print_regression_table(anxiety_percent_surprised_negative_sensitivityanalysis,
                        c("Intercept", "Baseline anxiety (z)"),
                       "Negative valence bias (z)")
```

## *Supplemental Table 9a: Negative valence biases and longitudinal anxiety scores.*
```{r anxiety_negativity_bias_longitudinal,include=FALSE}
anxiety_negativity_bias_longitudinal <- lmer(anxiety_total ~ participant_month +  Percent_Surprised_Negative_Z + (participant_month*Percent_Surprised_Negative_Z) + (1 + participant_month | Participant_ID), data = fullsample_long_questionnairedata)
#summary(anxiety_negativity_bias_longitudinal, ddf = "Kenward-Roger") 
#confint(anxiety_negativity_bias_longitudinal)
# No fixed effect of time or negativity biases. No interaction between time and negativity biases.
# interaction beta = 0.72, 95% CI [-0.02, 1.46], t(36.61) =  1.91, p =  0.06.
```

```{r anxiety_negativity_bias_longitudinal_table,echo=FALSE}
print_multilevel_table(anxiety_negativity_bias_longitudinal,
                        c("Intercept","Time (months)","Negative valence bias (z)","Time x Negative valence bias"),
                       "Anxiety score")

```

## *Supplemental Table 9b: Same model with low accuracy participant removed.*
```{r anxiety_negativity_bias_longitudinal_sensitivityanalysis,include=FALSE}
anxiety_negativity_bias_longitudinal_sensitivityanalysis <- lmer(anxiety_total ~ participant_month +  Percent_Surprised_Negative_Z + (participant_month*Percent_Surprised_Negative_Z) + (1 + participant_month | Participant_ID), data = subset(fullsample_long_questionnairedata,Participant_ID!="P_070"))
```

```{r anxiety_negativity_bias_longitudinal_sensitivityanalysis_table,echo=FALSE}

print_multilevel_table(anxiety_negativity_bias_longitudinal_sensitivityanalysis,
                        c("Intercept","Time (months)","Negative valence bias (z)","Time x Negative valence bias"),
                       "Anxiety score")

```

## *Supplemental Table 10a: Baseline anxiety and average reaction time to ambiguous stimuli.*
```{r anxiety_reactiontime,include=FALSE}
anxiety_reactiontime_surprised <- lm(surprised_rt_average_z ~ Anxiety_Total_T1_Z, data = data)
#summary(anxiety_reactiontime_surprised)
# not significant.
```

```{r anxiety_reactiontime_table,echo=FALSE}
print_regression_table(anxiety_reactiontime_surprised,
                        c("Intercept", "Baseline anxiety (z)"),
                       "Average RT to surprised images in post-scan task")

```

## *Supplemental Table 10b: Same model with low accuracy participant removed.*
```{r anxiety_reactiontime_sensitivityanalysis,include=FALSE}
anxiety_reactiontime_surprised_sensitivityanalysis <- lm(surprised_rt_average_z ~ Anxiety_Total_T1_Z, data = subset(data,Participant_ID!="P_070"))
#summary(anxiety_reactiontime_surprised)
# not significant.
```

```{r anxiety_reactiontime_sensitivityanalysis_table,echo=FALSE}
print_regression_table(anxiety_reactiontime_surprised_sensitivityanalysis,
                        c("Intercept", "Baseline anxiety (z)"),
                       "Average RT to surprised images in post-scan task")
```

# Condition-level analyses: Representational similarity (RS) and baseline anxiety.
```{r anxiety_rsa_amygdala,include=FALSE}

## Right amygdala. ##
 
# Angry/surprised.
right_amygdala_anxiety_angrysurprised <- lm(Anxiety_Total_T1_Z ~ AO_SUR_average_amy_R_Thr50_fisher_z, data = data)
#summary(right_amygdala_anxiety_angrysurprised)
# p = 0.72.
#plot(right_amygdala_anxiety_angrysurprised) # model diagnostics.

# Happy/surprised.
right_amygdala_anxiety_happysurprised <- lm(Anxiety_Total_T1_Z ~ HO_SUR_average_amy_R_Thr50_fisher_z, data = data)
#summary(right_amygdala_anxiety_happysurprised)
# p = 0.35.
#summary(right_amygdala_anxiety_happysurprised)
#confint(right_amygdala_anxiety_happysurprised, 'HO_SUR_average_amy_R_Thr50_fisher_z', level=0.95)
# estimate = -1.78; 95% CI[ -5.5,2.0]; t(39) =  -0.96; p = 0.35.

# Angry/happy.
right_amygdala_anxiety_angryhappy <- lm(Anxiety_Total_T1_Z ~ AO_HO_average_amy_R_Thr50_fisher_z, data = data)
#summary(right_amygdala_anxiety_angryhappy)

## Left amygdala. ##

# Angry/Surprised.
left_amygdala_anxiety_angrysurprised <- lm(Anxiety_Total_T1_Z ~ AO_SUR_average_amy_L_Thr50_fisher_z, data = data)
#summary(left_amygdala_anxiety_angrysurprised)
# p = 0.89.

# Happy/surprised.
left_amygdala_anxiety_happysurprised <- lm(Anxiety_Total_T1_Z ~ HO_SUR_average_amy_L_Thr50_fisher_z, data = data)
#summary(left_amygdala_anxiety_happysurprised)
#confint(left_amygdala_anxiety_happysurprised, 'HO_SUR_average_amy_L_Thr50_fisher_z', level=0.95)
# estimate = -4.030; 95% CI[-7.8, -0.3]; t(39) = -2.18; p = 0.035.
# Why are these beta coefficients so large (aren't they standardized?).

# Does the observed association hold when we control for participant-specific ROI size?
left_amygdala_anxiety_happysurprised_controlvoxels <- lm(Anxiety_Total_T1_Z ~ HO_SUR_average_amy_L_Thr50_fisher_z + number_voxels_amy_L_Thr50_average, data = data)
#summary(left_amygdala_anxiety_happysurprised_controlvoxels)
#confint(left_amygdala_anxiety_happysurprised_controlvoxels, 'HO_SUR_average_amy_L_Thr50_fisher_z', level=0.95)
# estimate = -4.02; 95% CI[-7.8, -0.24]; t(38) =-2.16; p = 0.038.

# Angry/happy.
left_amygdala_anxiety_angryhappy <- lm(Anxiety_Total_T1_Z ~AO_HO_average_amy_L_Thr50_fisher_z , data = data)
#summary(left_amygdala_anxiety_angryhappy)
#confint(left_amygdala_anxiety_angryhappy, 'Anxiety_Total_T1_Z', level=0.95)
# p = 0.46.
```

## *Supplemental Table 11: Ambiguous/threatening RS and baseline anxiety.*
### Right amygdala.
```{r anxiety_rsa_table_ambiguousthreatening_amygdala_right,echo=FALSE}
print_regression_table(right_amygdala_anxiety_angrysurprised,
                        c("Intercept", "Ambiguous/threatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")
```

### Left amygdala.
```{r anxiety_rsa_table_ambiguousthreatening_amygdala_left,echo=FALSE}
print_regression_table(left_amygdala_anxiety_angrysurprised,
                        c("Intercept", "Ambiguous/threatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")
```

## *Supplemental Table 12: Ambiguous/nonthreatening RS and baseline anxiety.*
### Right amygdala.
```{r anxiety_rsa_table_ambiguousnonthreatening_right,echo=FALSE}
print_regression_table(right_amygdala_anxiety_happysurprised,
                        c("Intercept", "Ambiguous/nonthreatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")

```

### Left amygdala.
```{r anxiety_rsa_table_ambiguousnonthreatening_left,echo=FALSE}
print_regression_table(left_amygdala_anxiety_happysurprised,
                        c("Intercept", "Ambiguous/nonthreatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")
```

### Left amygdala: Sensitivity analysis (Control voxels).
```{r anxiety_rsa_table_ambiguousnonthreatening_left_controlvoxels,echo=FALSE}
print_regression_table(left_amygdala_anxiety_happysurprised_controlvoxels,
                        c("Intercept", "Ambiguous/nonthreatening RS (Fisher z score)","Left amygdala size"),
                       "Baseline anxiety score (z)")

```

## *Supplemental Table 13: Threatening/nonthreatening RS and baseline anxiety.*
### Right amygdala.
```{r anxiety_rsa_table_threateningnonthreatening_right,echo=FALSE}

print_regression_table(right_amygdala_anxiety_angryhappy,
                        c("Intercept", "Threatening/nonthreatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")


```

### Left amygdala.
```{r anxiety_rsa_table_threateningnonthreatening_left,echo=FALSE}

print_regression_table(left_amygdala_anxiety_angryhappy,
                        c("Intercept", "Threatening/nonthreatening RS (Fisher z score)"),
                       "Baseline anxiety score (z)")
```

# Condition-level analyses: Representational similarity (RS) and longitudinal anxiety.
```{r anxiety_rsa_amygdala_longitudinal,include=FALSE}

## Right amygdala. ##
 anxiety_negativity_bias_longitudinal <- lmer(anxiety_total ~ participant_month +  Percent_Surprised_Negative_Z + (participant_month*Percent_Surprised_Negative_Z) + (1 + participant_month | Participant_ID), data = fullsample_long_questionnairedata)

# Angry/surprised.
right_amygdala_anxiety_angrysurprised_longitudinal <- lmer(anxiety_total ~ AO_SUR_average_amy_R_Thr50_fisher_z + participant_month +
                                                         (participant_month*AO_SUR_average_amy_R_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
#summary(right_amygdala_anxiety_angrysurprised_longitudinal)

# Happy/surprised.
right_amygdala_anxiety_happysurprised_longitudinal <- lmer(anxiety_total ~ HO_SUR_average_amy_R_Thr50_fisher_z  + participant_month +
                                                         (participant_month*HO_SUR_average_amy_R_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
#summary(right_amygdala_anxiety_happysurprised_longitudinal)

# Angry/happy.
right_amygdala_anxiety_angryhappy_longitudinal <- lmer(anxiety_total ~ AO_HO_average_amy_R_Thr50_fisher_z + participant_month +
                                                         (participant_month*AO_HO_average_amy_R_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
summary(right_amygdala_anxiety_angryhappy_longitudinal)

## Left amygdala. ##

# Angry/surprised.
left_amygdala_anxiety_angrysurprised_longitudinal <- lmer(anxiety_total ~ AO_SUR_average_amy_L_Thr50_fisher_z + participant_month +
                                                         (participant_month*AO_SUR_average_amy_L_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
#summary(left_amygdala_anxiety_angrysurprised_longitudinal)

# Happy/surprised.
left_amygdala_anxiety_happysurprised_longitudinal <- lmer(anxiety_total ~ HO_SUR_average_amy_L_Thr50_fisher_z  + participant_month +
                                                         (participant_month*HO_SUR_average_amy_L_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
#summary(left_amygdala_anxiety_happysurprised_longitudinal)

# Angry/happy.
left_amygdala_anxiety_angryhappy_longitudinal <- lmer(anxiety_total ~ AO_HO_average_amy_L_Thr50_fisher_z + participant_month +
                                                         (participant_month*AO_HO_average_amy_L_Thr50_fisher_z) + (1 + participant_month | Participant_ID),
                                                         data = fullsample_long_questionnairedata)
#summary(left_amygdala_anxiety_angryhappy_longitudinal)

```

## *Supplemental Table 14: Ambiguous/threatening RS and longitudinal anxiety.*
### Right amygdala.
```{r rsa_longitudinal_ambiguous_threatening_right,echo=FALSE}
print_multilevel_table(right_amygdala_anxiety_angrysurprised_longitudinal,
                        c("Intercept","Ambiguous/threatening RS (fisher z)","Time (months)","Time x Ambiguous/threatening RS"),
                       "Anxiety score")
```

### Left amygdala.
```{r rsa_longitudinal_ambiguous_threatening_left,echo=FALSE}
print_multilevel_table(left_amygdala_anxiety_angrysurprised_longitudinal,
                        c("Intercept","Ambiguous/threatening RS (fisher z)","Time (months)","Time x Ambiguous/threatening RS"),
                       "Anxiety score")
```

## *Supplemental Table 15: Ambiguous/nonthreatening RS and longitudinal anxiety.*
### Right amygdala.
```{r rsa_longitudinal_ambiguous_nonthreatening_right,echo=FALSE}
print_multilevel_table(right_amygdala_anxiety_happysurprised_longitudinal,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)","Time (months)","Time x Ambiguous/nonthreatening RS"),
                       "Anxiety score")
```

### Left amygdala.
```{r rsa_longitudinal_ambiguous_nonthreatening_left,echo=FALSE}
print_multilevel_table(left_amygdala_anxiety_happysurprised_longitudinal,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)","Time (months)","Time x Ambiguous/nonthreatening RS"),
                       "Anxiety score")
```

## *Supplemental Table 16: Threatening/nonthreatening RS and longitudinal anxiety.*
### Right amygdala.
```{r rsa_longitudinal_threatening_nonthreatening_right,echo=FALSE}
print_multilevel_table(right_amygdala_anxiety_angryhappy_longitudinal,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)","Time (months)","Time x Threatening/nonthreatening RS"),
                       "Anxiety score")
```

### Left amygdala.
```{r rsa_longitudinal_threatening_nonthreatening_left,echo=FALSE}
print_multilevel_table(left_amygdala_anxiety_angryhappy_longitudinal,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)","Time (months)","Time x Threatening/nonthreatening RS"),
                       "Anxiety score")
```

# Condition-level analyses: Representational similarity (RS) and negative valence biases.
```{r valencebias_rsa_amygdala,include=FALSE}

## Right amygdala. ##

# Angry/surprised.
right_amygdala_valencebias_angrysurprised  <- lm(Percent_Surprised_Negative_Z ~ AO_SUR_average_amy_R_Thr50_fisher_z,
                                                         data = data)
#summary(right_amygdala_valencebias_angrysurprised)

right_amygdala_valencebias_angrysurprised_sensitivityanalysis <- lm(Percent_Surprised_Negative_Z ~ AO_SUR_average_amy_R_Thr50_fisher_z,data = subset(data,Participant_ID!="P_070"))

#summary(right_amygdala_valencebias_angrysurprised_sensitivityanalysis)


# Happy/surprised.
right_amygdala_valencebias_happysurprised  <- lm(Percent_Surprised_Negative_Z ~ HO_SUR_average_amy_R_Thr50_fisher_z, data = data)
#summary(right_amygdala_valencebias_happysurprised)

right_amygdala_valencebias_happysurprised_sensitivityanalysis  <- lm(Percent_Surprised_Negative_Z ~ HO_SUR_average_amy_R_Thr50_fisher_z, data = subset(data,Participant_ID!="P_070"))
#summary(right_amygdala_valencebias_happysurprised_sensitivityanalysis)

# Angry/happy.
right_amygdala_valencebias_angryhappy  <- lm(Percent_Surprised_Negative_Z ~ AO_HO_average_amy_R_Thr50_fisher_z,data = data)
#summary(right_amygdala_valencebias_angryhappy)


# Angry/happy.
right_amygdala_valencebias_angryhappy_sensitivityanalysis  <- lm(Percent_Surprised_Negative_Z ~ AO_HO_average_amy_R_Thr50_fisher_z,
                                                        data = subset(data,Participant_ID!="P_070"))
#summary(right_amygdala_valencebias_angryhappy_sensitivityanalysis)


## Left amygdala. ##

# Angry/surprised.
left_amygdala_valencebias_angrysurprised <- lm(Percent_Surprised_Negative_Z ~ AO_SUR_average_amy_L_Thr50_fisher_z, data = data)
#summary(left_amygdala_valencebias_angrysurprised)

left_amygdala_valencebias_angrysurprised_sensitivityanalysis <- lm(Percent_Surprised_Negative_Z ~ AO_SUR_average_amy_L_Thr50_fisher_z, data = subset(data,Participant_ID!="P_070"))
#summary(left_amygdala_valencebias_angrysurprised_sensitivityanalysis)

# Happy/surprised.
left_amygdala_valencebias_happysurprised  <- lm(Percent_Surprised_Negative_Z ~ HO_SUR_average_amy_L_Thr50_fisher_z,
                                                         data = data)
#summary(left_amygdala_valencebias_happysurprised)

left_amygdala_valencebias_happysurprised_sensitivityanalysis  <- lm(Percent_Surprised_Negative_Z ~ HO_SUR_average_amy_L_Thr50_fisher_z, data = subset(data,Participant_ID!="P_070"))
#summary(left_amygdala_valencebias_happysurprised_sensitivityanalysis)

# Angry/happy.
left_amygdala_valencebias_angryhappy  <- lm(Percent_Surprised_Negative_Z ~ AO_HO_average_amy_L_Thr50_fisher_z, data = data)
#summary(left_amygdala_valencebias_angryhappy)

left_amygdala_valencebias_angryhappy_sensitivityanalysis <- lm(Percent_Surprised_Negative_Z ~ AO_HO_average_amy_L_Thr50_fisher_z,
                                                          data = subset(data,Participant_ID!="P_070"))
#summary(left_amygdala_valencebias_angryhappy_sensitivityanalysis)

```

## *Supplemental Table 17a: Ambiguous/threatening RS and negative valence biases.*
### Right amygdala.
```{r rsa_valencebias_ambiguous_threatening_right,echo=FALSE}
print_regression_table(right_amygdala_valencebias_angrysurprised,
                        c("Intercept","Ambiguous/threatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_ambiguous_threatening_left,echo=FALSE}
print_regression_table(left_amygdala_valencebias_angrysurprised,
                        c("Intercept","Ambiguous/threatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

## *Supplemental Table 17b: Same model with low accuracy participant removed.*
### Right amygdala.
```{r rsa_valencebias_ambiguous_threatening_right_sensitivityanalysis,echo=FALSE}
print_regression_table(right_amygdala_valencebias_angrysurprised_sensitivityanalysis,
                        c("Intercept","Ambiguous/threatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_ambiguous_threatening_left_sensitivityanalysis,echo=FALSE}
print_regression_table(left_amygdala_valencebias_angrysurprised_sensitivityanalysis,
                        c("Intercept","Ambiguous/threatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

## *Supplemental Table 18a: Ambiguous/nonthreatening RS and negative valence biases.*
### Right amygdala.
```{r rsa_valencebias_ambiguous_nonthreatening_right,echo=FALSE}
print_regression_table(right_amygdala_valencebias_happysurprised,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_ambiguous_nonthreatening_left,echo=FALSE}
print_regression_table(left_amygdala_valencebias_happysurprised,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

## *Supplemental Table 18b: Same model with low accuracy participant removed.*
### Right amygdala.
```{r rsa_valencebias_ambiguous_nonthreatening_right_sensitivityanalysis,echo=FALSE}
print_regression_table(right_amygdala_valencebias_happysurprised_sensitivityanalysis,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_ambiguous_nonthreatening_left_sensitivityanalysis,echo=FALSE}
print_regression_table(left_amygdala_valencebias_happysurprised_sensitivityanalysis,
                        c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

## *Supplemental Table 19a: Threatening/nonthreatening RS and negative valence biases.*
### Right amygdala.
```{r rsa_valencebias_threatening_nonthreatening_right,echo=FALSE}
print_regression_table(right_amygdala_valencebias_angryhappy,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_threatening_nonthreatening_left,echo=FALSE}
print_regression_table(left_amygdala_valencebias_angryhappy,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

## *Supplemental Table 19b: Same model with low accuracy participant removed.*
### Right amygdala.
```{r rsa_valencebias_threatening_nonthreatening_right_sensitivityanalysis,echo=FALSE}
print_regression_table(right_amygdala_valencebias_angryhappy_sensitivityanalysis,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

### Left amygdala.
```{r rsa_valencebias_threatening_nonthreatening_left_sensitivityanalysis,echo=FALSE}
print_regression_table(left_amygdala_valencebias_angryhappy_sensitivityanalysis,
                        c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                       "Negative valence bias (z score)")
```

# Single-trial (actor-level) analyses: Single trial (actor-level) RS and subsequent appraisals of the actor's ambiguous image.
```{r single_trial_rsa_predict_choices,include=FALSE}

rsa_surprised_trials <- subset(lss_data,Emotion == "surprised") # Only examine responses to surprised trials.
# Because their first run was cut a little short, do not have values for them for the single trial estimates (but do for the condition level ones).
#rsa_surprised_trials <- subset(rsa_surprised_trials,Participant_ID!="CTS026")
#participants <- subset(data, Participant_ID!="CTS026")
#participants <- participants$Participant_ID
#nrow(rsa_surprised_trials)/41 # 99 (for every participant, there should be one for every actor shown in the fMRI task).

##### Right amygdala. #####

# Angry/surprised.
right_amygdala_angry <- glmer(response ~ AO_SUR_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_angry)
# p = 0.12.

# Happy/surprised.
right_amygdala_happy <- glmer(response ~ HO_SUR_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_happy)
# p = 0.38.

# Angry/happy.
right_amygdala_angry_happy <- glmer(response ~ AO_HO_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_angry_happy)
# p = 0.51.


##### Left amygdala. #####
# Angry/surprised.
left_amygdala_angry <- glmer(response ~ AO_SUR_fisher_z_amygdala_left + (1 | Participant_ID),
                       data = rsa_surprised_trials, 
                       family = binomial(link="logit"),
                       control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_angry)
# p = 0.41.

# Happy/surprised.
left_amygdala_happy <- glmer(response ~ HO_SUR_fisher_z_amygdala_left + (1 | Participant_ID),
                             data = rsa_surprised_trials, 
                             family = binomial(link="logit"),
                             control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_happy)
# p = 0.31.

# Angry/happy.
left_amygdala_angry_happy <- glmer(response ~ AO_HO_fisher_z_amygdala_left + (1 | Participant_ID),
                             data = rsa_surprised_trials, 
                             family = binomial(link="logit"),
                             control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_angry_happy)
# beta = 0.92, z = 2.68, p = 0.0074.
# So the more overlap, the more likely to rate as positive.
coef(left_amygdala_angry_happy) # Intercepts should vary but beta values should not because only allowed for random intercepts here.
## odds ratios and 95% CI.
# Note: Odds ratio should be about 2.7 times the logit value (2.7*0.92 = 2.5).

#library(broom.mixed)
tidy(left_amygdala_angry_happy,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
# Odds ratio = 2.52; 95% CI [1.28, 4.94].

# Control for number of voxels.
left_amygdala_angry_happy_controlvoxels <- glmer(response ~ AO_HO_fisher_z_amygdala_left + 
                                     number_voxels_amygdala_left_Thr50 + (1 | Participant_ID),
                                   data = rsa_surprised_trials, 
                                   family = binomial(link="logit"),
                                   control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_angry_happy_controlvoxels)
tidy(left_amygdala_angry_happy_controlvoxels,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
# beta = 0.92, Odds ratio = 2.52; 95% CI [1.28, 4.94], z = 2.68, p = 0.0073.


```

## *Supplemental Table 20a: Actor-level ambiguous/threatening RS and subsequent appraisals of the actor's ambiguous image.*
### Right amygdala.
```{r single_trial_rsa_angrysurprised_right,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_angry,c("Intercept","Ambiguous/threatening RS (fisher z)"),"Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_angrysurprised_left,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_angry,
                                c("Intercept","Ambiguous/threatening RS (fisher z)"),
                                  "Left amygdala")

```

## *Supplemental Table 20b: Same model with low accuracy participant removed.*
```{r single_trial_rsa_predict_choices_sensitivityanalysis,include=FALSE}

rsa_surprised_trials <- subset(lss_data,Emotion == "surprised") # Only examine responses to surprised trials.
rsa_surprised_trials_sensitivityanalysis <- subset(rsa_surprised_trials, Participant_ID!="P_070")

# Because their first run was cut a little short, do not have values for them for the single trial estimates (but do for the condition level ones).
#rsa_surprised_trials <- subset(rsa_surprised_trials,Participant_ID!="CTS026")
#participants <- subset(data, Participant_ID!="CTS026")
#participants <- participants$Participant_ID
#nrow(rsa_surprised_trials)/41 # 99 (for every participant, there should be one for every actor shown in the fMRI task).

##### Right amygdala. #####

# Angry/surprised.
right_amygdala_angry_sensitivityanalysis <- glmer(response ~ AO_SUR_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials_sensitivityanalysis, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_angry)
# p = 0.12.

# Happy/surprised.
right_amygdala_happy_sensitivityanalysis <- glmer(response ~ HO_SUR_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials_sensitivityanalysis, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_happy)
# p = 0.38.

# Angry/happy.
right_amygdala_angry_happy_sensitivityanalysis <- glmer(response ~ AO_HO_fisher_z_amygdala_right + (1 | Participant_ID),
                              data = rsa_surprised_trials_sensitivityanalysis, 
                              family = binomial(link="logit"),
                              control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(right_amygdala_angry_happy)
# p = 0.51.


##### Left amygdala. #####
# Angry/surprised.
left_amygdala_angry_sensitivityanalysis <- glmer(response ~ AO_SUR_fisher_z_amygdala_left + (1 | Participant_ID),
                       data = rsa_surprised_trials_sensitivityanalysis, 
                       family = binomial(link="logit"),
                       control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_angry)
# p = 0.41.

# Happy/surprised.
left_amygdala_happy_sensitivityanalysis <- glmer(response ~ HO_SUR_fisher_z_amygdala_left + (1 | Participant_ID),
                             data = rsa_surprised_trials_sensitivityanalysis, 
                             family = binomial(link="logit"),
                             control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_happy)
# p = 0.31.

# Angry/happy.
left_amygdala_angry_happy_sensitivityanalysis <- glmer(response ~ AO_HO_fisher_z_amygdala_left + (1 | Participant_ID),
                             data = rsa_surprised_trials_sensitivityanalysis, 
                             family = binomial(link="logit"),
                             control = glmerControl(optimizer = "bobyqa"), nAGQ = 0)
#summary(left_amygdala_angry_happy)
# beta = 0.92, z = 2.68, p = 0.0074.
# So the more overlap, the more likely to rate as positive.
coef(left_amygdala_angry_happy_sensitivityanalysis) # Intercepts should vary but beta values should not because only allowed for random intercepts here.
## odds ratios and 95% CI.
# Note: Odds ratio should be about 2.7 times the logit value (2.7*0.92 = 2.5).

#library(broom.mixed)
tidy(left_amygdala_angry_happy_sensitivityanalysis,conf.int=TRUE,exponentiate=TRUE,effects="fixed")
# Odds ratio = 2.52; 95% CI [1.28, 4.94].


```

### Right amygdala.
```{r single_trial_rsa_angrysurprised_right_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_angry_sensitivityanalysis,c("Intercept","Ambiguous/threatening RS (fisher z)"),"Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_angrysurprised_left_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_angry_sensitivityanalysis,
                                c("Intercept","Ambiguous/threatening RS (fisher z)"),
                                  "Left amygdala")

```

## *Supplemental Table 21a: Actor-level ambiguous/nonthreatening RS and subsequent appraisals of the actor's ambiguous image.*
### Right amygdala.
```{r single_trial_rsa_happysurprised_right,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_happy,
                                c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                                  "Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_happysurprised_left,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_happy,
                                c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                                  "Left amygdala")
```

## *Supplemental Table 21b: Same model with low accuracy participant removed.*
### Right amygdala.
```{r single_trial_rsa_happysurprised_right_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_happy_sensitivityanalysis,
                                c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                                  "Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_happysurprised_left_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_happy_sensitivityanalysis,
                                c("Intercept","Ambiguous/nonthreatening RS (fisher z)"),
                                  "Left amygdala")
```

## *Supplemental Table 22a: Actor-level threatening/nonthreatening RS and subsequent appraisals of the actor's ambiguous image.*
### Right amygdala.
```{r single_trial_rsa_angryhappy_right,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_angry_happy,
                                c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                                  "Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_angryhappy_left,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_angry_happy,
                                c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                                  "Left amygdala")


```
### Left amygdala: Sensitivity analysis (Control voxels).
```{r single_trial_rsa_angryhappy_left_controlvoxels,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_angry_happy_controlvoxels,
                                c("Intercept","Threatening/nonthreatening RS (fisher z)", "Left amygdala voxel number"),
                                  "Left amygdala")
```

## *Supplemental Table 22b: Same model with low accuracy participant removed.*
### Right amygdala.
```{r single_trial_rsa_angryhappy_right_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(right_amygdala_angry_happy_sensitivityanalysis,
                                c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                                  "Right amygdala")

```
### Left amygdala.
```{r single_trial_rsa_angryhappy_left_sensitivityanalysis,echo=FALSE,warning=FALSE}

print_multilevel_logistic_table(left_amygdala_angry_happy_sensitivityanalysis,
                                c("Intercept","Threatening/nonthreatening RS (fisher z)"),
                                  "Left amygdala")


```

# Supplemental figures.
## *Supplemental Figure 1: Visualization of study timepoints.*
```{r overall_timepoint_plot, echo=FALSE, warning = FALSE}

fullsample_long_questionnairedata$Participant_ID <- as.factor(fullsample_long_questionnairedata$Participant_ID)
fullsample_long_questionnairedata$questionnaire_date <- as.Date(fullsample_long_questionnairedata$questionnaire_date) 
fullsample_long_questionnairedata$participantordered <- fct_rev(fullsample_long_questionnairedata$Participant_ID) # Relevel for graph.


overall_timepoint_graph <- ggplot(fullsample_long_questionnairedata,aes(x=overall_timepoint,y=participantordered, group = participantordered))+
  geom_point(size=2) +
  geom_line(size=.7) + 
  ylab("\nParticipants") +
  xlab("Days since beginning of study\n") +
  scale_x_continuous(breaks = seq(0,300,20)) +
  theme(plot.title = element_blank(),
        axis.title.x= element_text(size=15, vjust=-0.3, face="bold"),
        axis.title.y= element_text(size=15, vjust=1.5, face="bold"),
        axis.text.x= element_text(size=14, colour="black"),
        axis.text.y= element_blank(),
        axis.ticks.y=element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"))

overall_timepoint_graph

```

## *Supplemental Figure 2: Individual anxiety scores over time.*
```{r longitudinal_anxiety_plot, echo=FALSE, warning = FALSE}
supplemental_figure_1 <- ggplot(fullsample_long_questionnairedata, aes(x=as.integer(timepoint_number), y=anxiety_total, group=factor(Participant_ID))) + 
  geom_line() + 
  guides(colour=FALSE) + 
  xlab("Time Point") +
  ylab("Anxiety Total") + aes(colour = factor(Participant_ID)) + ylim(0,80) + 
  geom_hline(yintercept = 23, size = 2, color = "gray40", linetype = "dotted") +
  scale_x_continuous(limits = c(1,5),expand = c(0.05, 0.05), minor_breaks = c(1,2,3), n.breaks = 5) +
  nsh_theme

supplemental_figure_1 

# Do this if want to fit a line to the data.
# ggplot(fullsample_long_questionnairedata, aes(x=participant_specific_timepoint, y=anxiety_total, group=factor(Participant_ID))) + 
#   geom_smooth(method = "lm",se = FALSE) +
#   guides(colour=FALSE) + 
#   xlab("Participant-Specific Time Point (Days)") +
#   ylab("Anxiety Total") + aes(colour = factor(Participant_ID)) + ylim(0,80) + 
#   geom_hline(yintercept = 23, size = 2, color = "gray40", linetype = "dotted") +
#   nsh_theme

```

## *Supplemental Figure 3a: Accuracy for non-ambiguous (threatening and nonthreatening) trials in post-scan task.*
```{r angry_happy_accuracy,echo=FALSE, warning = FALSE}

# Plot accuracy for angry (percent categorized as negative) and happy (percent categorized as positive) trials in post-scan task.

accuracy_data <- data %>% select(Participant_ID, Percent_Angry_Correct, Percent_Happy_Correct) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "accuracy")

accuracy_data$trial_type <- str_replace(accuracy_data$trial_type, "Percent_", "")
accuracy_data$trial_type <- str_replace(accuracy_data$trial_type, "_Correct", "")


angry_happy_accuracy_plot <- ggplot(accuracy_data,aes(x = trial_type, y = accuracy)) + 
  geom_bar(stat="identity",fill="gray80",alpha=0.5) +
  geom_jitter(aes(colour = Participant_ID), size = 6, width = 0.25, alpha = 0.4) + 
  scale_y_continuous(limits = c(0.00,1.00),breaks = seq(0,1,0.25)) +
  nsh_theme + 
  theme(legend.position = "none") +
  labs(title = "Accuracy for non-ambiguous (angry and happy) trials in post-scan task",
       subtitle = "Angry = percent categorized as negative\nHappy = percent categorized as positive",
       x = "Trial type\n",
       y = "Accuracy")

angry_happy_accuracy_plot

```

## *Supplemental Figure 3b: Reaction time by trial type in post-scan task.*
```{r angry_happy_reactiontime_plot,echo=FALSE, warning = FALSE}

# Plot reaction time by trial type in post-scan task.
# Add standard deviations?

reactiontime_average_data <- data %>% select(Participant_ID, angry_rt_average, happy_rt_average,surprised_rt_average) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_average")

reactiontime_sd_data <- data %>% select(Participant_ID, angry_rt_sd, happy_rt_sd, surprised_rt_sd) %>%
  pivot_longer(!Participant_ID, names_to = "trial_type", values_to = "reactiontime_sd")

reactiontime_average_data$trial_type <- str_replace(reactiontime_average_data$trial_type, "_rt_average", "")
reactiontime_average_data$trial_type <- as.factor(reactiontime_average_data$trial_type)
reactiontime_sd_data$trial_type <- str_replace(reactiontime_sd_data$trial_type, "_rt_sd", "")
reactiontime_sd_data$trial_type <- as.factor(reactiontime_sd_data$trial_type)

reactiontime_data <- merge(reactiontime_average_data,reactiontime_sd_data,by=c("Participant_ID","trial_type"))

#reactiontime_by_trialtype <- lm(reactiontime_average ~ trial_type, data = reactiontime_data)
#summary(reactiontime_by_trialtype)

reactiontime_by_trialtype_plot <- ggplot(reactiontime_data,aes(x = trial_type, y = reactiontime_average)) + 
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(aes(colour = Participant_ID), size = 6, width = 0.25, alpha = 0.4) +
  #  geom_errorbar(aes(ymin=reactiontime_average - reactiontime_sd,
 #                  ymax=reactiontime_average + reactiontime_sd, color= Participant_ID), width=.2) +
  nsh_theme + 
  theme(legend.position = "none") +
  labs(title = "Average reaction time by trial type in post-scan task",
       x = "Trial type\n",
       y = "Average reaction time (seconds)")

reactiontime_by_trialtype_plot


```

## *Supplemental Figure 4: Negative valence biases in sample (percent surprised faces categorized negatively in post-scan task).*
```{r negativity_biases,echo=FALSE, warning = FALSE}
negative_interpretations <- data$Percent_Surprised_Negative
h<-hist(negative_interpretations, breaks=50, col="gray80", xlab="Proportion of Surprised Faces Categorized as Negative (Within Participant)",
        ylab="Number of Participants",
        main="Negative Interpretations of Ambiguous Stimuli",
        xlim=c(0.0,1.0),
        ylim=c(0,8))
axis(side=1, at=seq(0.0,1.0, 0.1))
xfit<-seq(min(negative_interpretations),max(negative_interpretations),length=40)
yfit<-dnorm(xfit,mean=mean(negative_interpretations),sd=sd(negative_interpretations))
yfit <- yfit*diff(h$mids[1:2])*length(negative_interpretations)
lines(xfit, yfit, col="#8AAB98", lwd=4)

```

## *Supplemental Figure 5: Percentage of participants that categorized each actor’s surprised face negatively.*
```{r actor_percent_negative,echo=FALSE, warning = FALSE}
actor_angry_images <- subset(actor_image_details,Emotion == "angry")
actor_angry_images$Actor <- as.factor(actor_angry_images$Actor)
actor_surprised_images <- subset(actor_image_details,Emotion == "surprised")
actor_surprised_images$Actor <- as.factor(actor_surprised_images$Actor)
actor_happy_images <- subset(actor_image_details,Emotion == "happy")
actor_happy_images$Actor <- as.factor(actor_happy_images$Actor)

# Plot percent of participants categorized each actor’s surprised face as negative.
actor_percent_negative_ratings_plot <- ggplot(actor_surprised_images,aes(x = reorder(Actor,image_taskbased_percent_negative_ratings), y = image_taskbased_percent_negative_ratings)) + 
  geom_bar(stat="identity",fill="gray80",alpha=0.5) +
  scale_y_continuous(limits = c(0.00,1.00),breaks = seq(0,1,0.25)) +
  actor_plots_theme +
  labs(title = "Percent negative interpretations for each actor",
       subtitle = "Surprised trials only",
       x = "Actor\n",
       y = "Percent of participants who categorized image negatively")

actor_percent_negative_ratings_plot
```

## *Supplemental Figure 6: Reaction times by actor and expression type in post-scan task.*
```{r actor_reaction_times,echo=FALSE, warning = FALSE}
# Plot means and standard deviations of reaction times for each actor for each expression type.
# Are these definitely in seconds? Seems fast, as none appear to take longer than one second.

actor_rt_angry_ratings_plot <- ggplot(subset(actor_angry_images,!is.na(image_taskbased_rt_average)),aes(x = reorder(Actor,image_taskbased_rt_average), y = image_taskbased_rt_average)) + 
  geom_bar(stat="identity",fill="gray80",alpha=0.5) +
  geom_errorbar(aes(ymin=image_taskbased_rt_average - image_taskbased_rt_sd,
                    ymax=image_taskbased_rt_average + image_taskbased_rt_sd), color= "#8AAB98", width=.2) +
  actor_plots_theme +
  labs(title = "Reaction times on angry trials for each actor",
       subtitle = "Angry trials",
       x = "Actor\n",
       y = "Reaction time (seconds)")

actor_rt_angry_ratings_plot


actor_rt_happy_ratings_plot <- ggplot(subset(actor_happy_images,!is.na(image_taskbased_rt_average)),aes(x = reorder(Actor,image_taskbased_rt_average), y = image_taskbased_rt_average)) + 
  geom_bar(stat="identity",fill="gray80",alpha=0.5) +
  geom_errorbar(aes(ymin=image_taskbased_rt_average - image_taskbased_rt_sd,
                    ymax=image_taskbased_rt_average + image_taskbased_rt_sd), color= "#8AAB98", width=.2) +
  actor_plots_theme +
  labs(title = "Reaction times on happy trials for each actor",
       subtitle = "Happy trials",
       x = "Actor\n",
       y = "Reaction time (seconds)")

actor_rt_happy_ratings_plot

actor_rt_surprised_ratings_plot <- ggplot(actor_surprised_images,aes(x = reorder(Actor,image_taskbased_rt_average), y = image_taskbased_rt_average)) + 
  geom_bar(stat="identity",fill="gray80",alpha=0.5) +
  geom_errorbar(aes(ymin=image_taskbased_rt_average - image_taskbased_rt_sd,
                    ymax=image_taskbased_rt_average + image_taskbased_rt_sd), color= "#8AAB98", width=.2) +
  actor_plots_theme +
  labs(title = "Reaction times on surprised trials for each actor",
       subtitle = "Surprised trials",
       x = "Actor\n",
       y = "Reaction time (seconds)")

actor_rt_surprised_ratings_plot

```

## *Supplemental Figure 7: Average RS values within the right and left amygdala by comparison type.*
```{r rsa_boxplot,echo=FALSE, warning = FALSE}

figuredata_long <- data[,grepl(glob2rx('Participant_ID|*average_amy*fisher_z'), names(data))] # Only keep these columns for the descriptive statistics table.
figuredata_long <- melt(figuredata_long,id.vars = 'Participant_ID', value.name = 'fisher_z')

figuredata_long <- figuredata_long %>%
  mutate(hemisphere =
           case_when(grepl("_R_",figuredata_long$variable) ~ "right",
                     grepl("_L_",figuredata_long$variable) ~ "left"),
         comparison = 
           case_when(grepl("AO_HO",figuredata_long$variable) ~ "threatening/nonthreatening",
                     grepl("AO_SUR",figuredata_long$variable) ~ "threatening/ambiguous",
                     grepl("HO_SUR",figuredata_long$variable) ~ "nonthreatening/ambiguous"))

factor_columns <- names(figuredata_long)[!(names(figuredata_long) %in% 'fisher_z')] # Make every column except fisher_z column a factor.
figuredata_long[,factor_columns] <- lapply(figuredata_long[,factor_columns], as.factor)

supplemental_boxplot_figure <- ggplot(figuredata_long, aes(fill= comparison, color = comparison, y = fisher_z, x = comparison)) + 
  geom_boxplot(outlier.shape = NA) +
  geom_jitter(shape = 1, size = 2, width = 0.05, color = "black") +
  scale_y_continuous(breaks = c(0.1,0.3,0.5,0.7,0.9)) +
  scale_colour_manual(values = condition_comparison_colors,guide = "none") +
  scale_fill_manual("Condition-level comparison type",values = condition_comparison_colors) +
  facet_grid(cols = vars(hemisphere)) +
  labs(title= "Condition-level similarity values by comparison type",
       subtitle = "Amygdala",
       y = "\nFisher Z Value",
       x = "\n") +
  theme(panel.spacing = unit(2, "lines"),
        text = element_text(size=8),
        axis.title.x = element_text(size=10),
        axis.title.y = element_text(size=8),
        strip.text = element_text(size=8),
        axis.text.x = element_blank(),
        axis.text.y = element_text(size=8),
        axis.ticks.x = element_blank(),
        legend.text = element_text(size=8),
        #legend.title = element_text(size=8),
        legend.title = element_blank(), # Since title has this information, can remove the legend title.
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        legend.position="bottom") # Move legend to below plot for this graph to give the plot itself more space.
  

supplemental_boxplot_figure 
```

## *Supplemental Figure 8: Distribution of RS values by condition comparison type and by actor.*
```{r actor_rsa_values,echo=FALSE, warning = FALSE}
actor_rsa_long <- subset(lss_data, Emotion == "surprised") # Only consider surprised images for now (the RSA values repeats three times per participant, once for every actor's trial).
actor_rsa_long <- actor_rsa_long[,grepl(glob2rx('Actor|*fisher_z_amygdala*'), names(actor_rsa_long))] # Only keep these columns for the descriptive statistics table.
actor_rsa_long <- actor_rsa_long %>% select(-c(Actor.Emotion)) # Remove this columns for now.

actor_rsa_summaries <- actor_rsa_long %>% group_by(Actor) %>%
                    summarise(
                      mean_AO_SUR_right = mean(AO_SUR_fisher_z_amygdala_right, na.rm = TRUE),
                      sd_AO_SUR_right = sd(AO_SUR_fisher_z_amygdala_right, na.rm = TRUE),
                      mean_HO_SUR_right = mean(HO_SUR_fisher_z_amygdala_right, na.rm = TRUE),
                      sd_HO_SUR_right = sd(HO_SUR_fisher_z_amygdala_right, na.rm = TRUE),
                      mean_AO_HO_right = mean(AO_HO_fisher_z_amygdala_right, na.rm = TRUE),
                      sd_AO_HO_right = sd(AO_HO_fisher_z_amygdala_right, na.rm = TRUE),
                      mean_AO_SUR_left = mean(AO_SUR_fisher_z_amygdala_left, na.rm = TRUE),
                      sd_AO_SUR_left = sd(AO_SUR_fisher_z_amygdala_left, na.rm = TRUE),
                      mean_HO_SUR_left = mean(HO_SUR_fisher_z_amygdala_left, na.rm = TRUE),
                      sd_HO_SUR_left = sd(HO_SUR_fisher_z_amygdala_left, na.rm = TRUE),
                      mean_AO_HO_left = mean(AO_HO_fisher_z_amygdala_left, na.rm = TRUE),
                      sd_AO_HO_left = sd(AO_HO_fisher_z_amygdala_left, na.rm = TRUE))
  
#nrow(actor_rsa_summaries) # 100, because it includes BM06 (only included in behavioral task).
actor_rsa_summaries <- subset(actor_rsa_summaries,Actor!="BM06")

## Right amygdala.

# Threatening/ambiguous RSA values.
right_AO_SUR_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_AO_SUR_right), y = mean_AO_SUR_right)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["threatening/ambiguous"]]) +
  geom_errorbar(aes(ymin = mean_AO_SUR_right - sd_AO_SUR_right,
                    ymax = mean_AO_SUR_right + sd_AO_SUR_right), width=.2) +
  actor_plots_theme +
   theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "\nTrial-level, within-participant RSA values by actor\nThreatening/ambiguous RSA values",
       subtitle = "Right amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")

right_AO_SUR_plot

# Nonthreatening/ambiguous RSA values.
right_HO_SUR_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_HO_SUR_right), y = mean_HO_SUR_right)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["nonthreatening/ambiguous"]]) +
  geom_errorbar(aes(ymin = mean_HO_SUR_right - sd_HO_SUR_right,
                    ymax = mean_HO_SUR_right + sd_HO_SUR_right), width=.2) +
  actor_plots_theme +
  theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "\nTrial-level, within-participant RSA values by actor\nNonthreatening/ambiguous RSA values",
       subtitle = "Right amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")

right_HO_SUR_plot

# Threatening/nonthreatening RSA values.
right_AO_HO_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_AO_HO_right), y = mean_AO_HO_right)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["threatening/nonthreatening"]]) +
  geom_errorbar(aes(ymin = mean_AO_HO_right - sd_AO_HO_right,
                    ymax = mean_AO_HO_right + sd_AO_HO_right), width=.2) +
  actor_plots_theme +
  theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "\nTrial-level, within-participant RSA values by actor\nThreatening/nonthreatening RSA values",
       subtitle = "Right amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")

right_AO_HO_plot

## Left amygdala.

# Threatening/ambiguous RSA values.
left_AO_SUR_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_AO_SUR_left), y = mean_AO_SUR_left)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["threatening/ambiguous"]]) +
  geom_errorbar(aes(ymin = mean_AO_SUR_left - sd_AO_SUR_left,
                    ymax = mean_AO_SUR_left + sd_AO_SUR_left), width=.2) +
  actor_plots_theme +
   theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
    labs(title = "\nTrial-level, within-participant RSA values by actor\nThreatening/ambiguous RSA values",
       subtitle = "Left amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")
 
left_AO_SUR_plot

# Nonthreatening/ambiguous RSA values.
left_HO_SUR_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_HO_SUR_left), y = mean_HO_SUR_left)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["nonthreatening/ambiguous"]]) +
  geom_errorbar(aes(ymin = mean_HO_SUR_left - sd_HO_SUR_left,
                    ymax = mean_HO_SUR_left + sd_HO_SUR_left), width=.2) +
  actor_plots_theme +
  theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
  labs(title = "\nTrial-level, within-participant RSA values by actor\nNonthreatening/ambiguous RSA values",
       subtitle = "Left amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")

left_HO_SUR_plot

# Threatening/nonthreatening RSA values.
left_AO_HO_plot <- ggplot(actor_rsa_summaries,aes(x = reorder(Actor,mean_AO_HO_left), y = mean_AO_HO_left)) + 
  geom_bar(stat="identity",fill=condition_comparison_colors[["threatening/nonthreatening"]]) +
  geom_errorbar(aes(ymin = mean_AO_HO_left - sd_AO_HO_left,
                    ymax = mean_AO_HO_left + sd_AO_HO_left), width=.2) +
  actor_plots_theme +
  theme(axis.title.x = element_text(size=16),
        axis.title.y = element_text(size=15),
        strip.text = element_text(size=15),
        axis.text.y = element_text(size=15),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black")) +
     labs(title = "\nTrial-level, within-participant RSA values by actor\nThreatening/nonthreatening RSA values",
       subtitle = "Left amygdala",
       x = "Actor\n",
       y = "\nRSA values (fisher z)")

left_AO_HO_plot

```

```{r participant_data,include=FALSE}
## P_070 (participant with 46% accuracy on angry trials).

participant <- subset(long_behavioral_data, Participant_ID == "P_070")
# Order by block and within-block trial, then from there number trials (across the entire task, not just within block).
participant <- participant %>% arrange(withinparticipant_blocknumber,withinblock_trialnumber)
participant$withintask_trialnumber <- as.numeric(rownames(participant))


# Plot responses.

# Line for happy, line for angry, line for surprised.
# Trial number on x axis.
# Response (0 or 1) on y axis.

# positive rating = 0 and a negative rating = 1.

participant_plot_data <- participant %>% select(TrialType,response,withintask_trialnumber)

#ggplot(participant_plot_data, aes(x=withintask_trialnumber, y=response, group=TrialType)) +
#  geom_line(aes(color=TrialType))+
#  geom_point(aes(color=TrialType))


ggplot(subset(participant_plot_data, TrialType == "happy"), aes(x=withintask_trialnumber, y=response)) +
  geom_line()+
  geom_point(size = 4) + 
  scale_y_continuous(limits = c(0.00,1.00),breaks = seq(0,1,0.25)) +
  nsh_theme + 
  theme(legend.position = "none") +
  labs(title = "Participant P_070: Ratings for happy trials in post-scan task",
       subtitle = "positive rating = 0 and a negative rating = 1",
       x = "Trial number\n",
       y = "Rating")


ggplot(subset(participant_plot_data, TrialType == "angry"), aes(x=withintask_trialnumber, y=response)) +
  geom_line()+
  geom_point(size = 4) + 
  scale_y_continuous(limits = c(0.00,1.00),breaks = seq(0,1,0.25)) +
  nsh_theme + 
  theme(legend.position = "none") +
  labs(title = "Participant P_070: Ratings for angry trials in post-scan task",
       subtitle = "positive rating = 0 and a negative rating = 1",
       x = "Trial number\n",
       y = "Rating")


ggplot(subset(participant_plot_data, TrialType == "surprised"), aes(x=withintask_trialnumber, y=response)) +
  geom_line()+
  geom_point(size = 4) + 
  scale_y_continuous(limits = c(0.00,1.00),breaks = seq(0,1,0.25)) +
  nsh_theme + 
  theme(legend.position = "none") +
  labs(title = "Participant P_070: Ratings for surprised trials in post-scan task",
       subtitle = "positive rating = 0 and a negative rating = 1",
       x = "Trial number\n",
       y = "Rating")









```

